Analysis of Information Security Job Advertisements

### 2020-05-17 paper/paper.tex
Add some text about detail pages.

\subsection{Evaluation of Scraping Tools}
\label{sub:evaluation_of_scraping_tools}

@@

As already briefly mentioned in \autoref{sub:evaluation_of_scraping_tools}, our goal was to implement scraping for \textit{Monster} (\href{https://www.monster.at/}{\texttt{monster.at}}), \textit{Indeed} (\href{https://at.indeed.com/}{\texttt{at.indeed.com}}) and \textit{StepStone} (\href{https://www.stepstone.at/}{\texttt{stepstone.at}}). In this section we will go into more detail about the exact steps which were necessary to reliably scrape each respective website.

@@

@@

@@

>>>>

\section{Evaluation of Scraping Tools}
\label{sec:evaluation_of_scraping_tools}

@@

As already briefly mentioned in \autoref{sec:evaluation_of_scraping_tools}, our goal was to implement scraping for \textit{Monster} (\href{https://www.monster.at/}{\texttt{monster.at}}), \textit{Indeed} (\href{https://at.indeed.com/}{\texttt{at.indeed.com}}) and \textit{StepStone} (\href{https://www.stepstone.at/}{\texttt{stepstone.at}}). In this section we will go into more detail about the exact steps which were necessary to reliably scrape each respective website.

@@

For the second part, the detail page of the job advertisement, we could now loop through all URLs and extract information from each one. On \textit{Monster}, each detail page contains the job title and a subtitle. The subtitle usually contains the location of the open position. Additionally, there is a sidebar which contains further metadata like the contract type, category, carreer level and publication date. The main content of the job advertisement is embedded into a nested \texttt{iframe} element. As mentioned in \autoref{sec:evaluation_of_scraping_tools}, using \textit{Selenium}, we could easily extract the content of this \texttt{iframe} element using the \texttt{switch\_to} function. All other data we could extract equally easily by selecting the corresponding elements using CSS selectors.

@@

Similarly to \textit{Monster}, the detail pages on \textit{Indeed} contain the title of the job advertisement as well as a metadata section. Care has to be taken when extracting data from this metadata section, since not every detail page contains every entry. Most pages seem to contain the location, but only some contain the contract type of the open position. For this reason, we simply treat all of these as optional and ignore any \texttt{NoSuchElementError} when searching for the respective element. In contrast to \textit{Monster}, the main content of the advertisement is contained as plain text, so no special treatment is necessary in this case.

@@

A detail page on \textit{StepStone} contains the job title at the top, followed by a metadata section. The metadata contains the location, type of contract and type of employment (i.e. full-time or part-time). The main content of the job advertisement, similarly to \textit{Indeed}, is a section containing plain text. This makes it trivial to extract all data.

\subsubsection{Detail Page}
\label{subsub:stepstone}
